MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-06 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
note DREAM

---
title: "MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model"
author: "Kelsey Montgomery"
date: "11/8/2019"
output: html_document
---

@@

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd",
                                 parentId ="syn9872607",
                                 folderName = "MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model")
```

@@

# Code
CODE <- Folder(name = "MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model", parentId = parentId)
CODE <- synStore(CODE)

>>>>

---
title: "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model"
author: "Kelsey Montgomery"
date: "`r date()`"
output: html_document
---

@@

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd",
                                 parentId ="syn9872607",
                                 folderName = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model")
```

@@

# Code
CODE <- Folder(name = "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model", parentId = parentId)
CODE <- synStore(CODE)
